\newglossaryentry{Detection Rate}
{
	name = {Detection Rate},
	description = {
		$$\frac{TP}{TP+FN}$$
		Synonomous with Sensitivity and True Positive Rate.
	},
	see=[synonomous with]{Sensitivity},
}

\newglossaryentry{False Positive Rate}
{
	name = {False Positive},
	description = {
		$$\frac{FP}{FP+TN}$$
	},
}



\newglossaryentry{Floating Car Data}
{
	name = Floating Car Data,
	description = {Floating car data (FCD) in traffic engineering and management is typically timestamped geo-localization and speed data directly collected by moving vehicles, in contrast to traditional traffic data collected at a fixed location by a stationary device or observer.}
}

\newglossaryentry{Loop Detector}
{
        name=Loop Detector,
        description={A buried wire loop with a magnetic field that the vehicle going overhead disrupts, detecting the car.  Does not detect pedestrians or animals.  }
}

\newglossaryentry{Macroscopic Traffic Variables}
{
	name = Macroscopic Traffic Variables,
	description = {
		Variables related to traffic, like intensity, density, and speed.
	},
	see = {Microscopic Traffic Variables}
}

\newglossaryentry{Microscopic Traffic Variables}
{
	name = Microscopic Traffic Variables,
	description = {
		Variables related to an individual driver, like speed, time, distance headway, time headway, vehicle type.
	},
	see = {Macroscopic Traffic Variables}
}

\newglossaryentry{Sensitivity}
{
	name = {Sensitivity},
	description = {
		$$\frac{TP}{TP+FN}$$
		Synonomous with Detection Rate and True Positive Rate.
	},
	see=[synonomous with]{True Positive Rate},
}

\newglossaryentry{Specificity}
{
	name = {Specificity},
	description = {
		$$\frac{TN}{TN+FP}$$
	},
	see = [synonomous with]{True Negative Rate}
}

\newglossaryentry{Traffic Oscillation}
{
	name = Traffic Oscillation,
	description = {
		The traffic oscillation is an important feature of traffic flow. It refers to the phenomenon that instead of maintaining a comfortable and stable driving status, vehicles are often forced to repeatedly accelerate and decelerate.
	}
}

\newglossaryentry{True Negative Rate}
{
	name = True Negative Rate,
	description = {
		$$\frac{TN}{TN+FP}$$
	},
	see = [synonomous with]{Specificity}
}

\newglossaryentry{True Positive Rate}
{
	name = True Positive Rate,
	description = {
		$$\frac{TP}{TP+FN}$$
		Synonomous with Sensitivity and Detection Rate.
	},
	see = [synonomous with]{Sensitivity}
}

\newacronym{ADAS}{ADAS}{Advanced Driver Assistance System}

\newacronym{FAR}{FAR}{False Alarm Rate}

\newacronym{R-CNN}{R-CNN}{Regional-Convolutional Neural Network}

\newacronym{TTC}{TTC}{Time to Collision}

\newacronym{DRAC}{DRAC}{Deceleration Rate to Avoid Crash}